
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19. 
```{r}
library(gganimate)
library(gifski)
library(tidyverse)

df <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

```
```{r}
head(df)
```
```{r}
library(lubridate)
df$Month <-  factor(month(df$Date_reported, label = TRUE))

d1 <- df %>% group_by(Month, Country) %>% summarise(mean = mean(Cumulative_deaths, na.rm=TRUE))
d2 <- d1 %>% group_by(Month) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 10)

a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col() +
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month:  {closest_state}', x='', y='Total Deaths', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank(), legend.position = "none") + 
    transition_states(Month)+
    ease_aes("cubic-in-out")

animate(a1, nframes = 400)
```


2. Make another bar race using that dataset.  

```{r}
d1 <- df %>% group_by(Month, Country) %>% summarise(mean = mean(New_cases, na.rm=TRUE))
d2 <- d1 %>% group_by(Month) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 10)

a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col() +
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Month:  {closest_state}', x='', y='New Cases', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank(), legend.position = "none") + 
    transition_states(Month)+
    ease_aes("cubic-in-out")

animate(a1, nframes = 400)
```


3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar race from ones in the slides. 

```{r}
df <- read_csv("https://covidtracking.com/data/download/all-states-history.csv")

tail(df)
```
```{r}
#hospitalized cumulative 2020 in NE



df$Year <-  factor(year(df$date))
df$Month <-  factor(month(df$date))



d1 <- df %>% 
  filter(state %in% c("RI", "ME", "NH", "MA", "CT", "VT"), Year == 2020)%>% 
  group_by(Month, state) %>% 
  summarise(mean = max(hospitalizedCumulative)) 
d2 <- d1 %>% 
  group_by(Month) %>% 
  mutate(rank=rank(-mean))

p1 <- d2 %>% 
  ggplot(aes(y=factor(rank), 
             x=mean, group=state, 
             fill=state)) + 
  geom_col()+
  transition_states(Month)+
  labs(x = 'Total Hospitalizations', 
       title = 'Month : {closest_state} , 2020')
animate(p1, nframes=100)

```


