
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 

```{r}
library(tidyverse)

df <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")
tail(df)
```


Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths
```{r}
max(df$Date_reported)
```


```{r}
df %>% filter(Date_reported == '2021-10-25') %>% arrange(-Cumulative_deaths)
```


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths

```{r}
library(gganimate)
library(ggplot2)
library(lubridate)

df %>% 
  filter(Country %in% c('India','Russian Federation', 'Indonesia')) %>% 
  ggplot(aes(y=Cumulative_cases,
            x=Date_reported,
            color=Country))+ 
  geom_line()+
  transition_reveal(Date_reported)
```


3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 

```{r}
df$death_per_cases = df$Cumulative_deaths / df$Cumulative_cases
df %>% filter(Date_reported == '2021-10-25') %>% arrange(-death_per_cases)

```


4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 

```{r}
df %>% 
  filter(Country %in% c('United States of America','Italy', 'Mexico')) %>% 
  ggplot(aes(y=death_per_cases,
            x=Date_reported,
            color=Country))+ 
  geom_line()+
  transition_reveal(Date_reported)
```


5. Use `transition_reveal` to create three animated graph with the vaccination data at 

https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv

```{r}
df <- read_csv("https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv")

tail(df, 20)
```
```{r}
# Vaccine Doses Administered Growth in 2021

library(lubridate)
df$Month <-  factor(month(df$Date))
df$Month <- as.numeric(as.character(df$Month))
df$Year <-  factor(year(df$Date))


d2 <- df %>% filter(Vaccine_Type == c('All'), Year == 2021) %>% group_by(Month,Vaccine_Type) %>% summarise(doses = mean(Doses_admin))

# Plot from the newly create data
d2 %>% ggplot()+geom_line(mapping=aes(x=Month, y=doses, color=Vaccine_Type)) + labs(x='Month', 
       y = 'Vaccines Administered', 
       title = 'Monthly Growth in Vaccine Doses Administered') + 
  transition_reveal(Month)
```
```{r}
df %>% 
  filter(Province_State %in% c('California','Texas', 'Florida'), Year == 2021) %>% group_by (Province_State, Month) %>% summarize(Doses_sum = sum(Doses_admin)) %>% 
  ggplot(aes(y=Doses_sum,
            x=Month,
            color=Province_State))+ 
  geom_line()+
  transition_reveal(Month)
```
```{r}
df %>% 
  filter(Province_State %in% c('California','Texas', 'Florida')) %>% 
  ggplot(aes(y=Doses_admin,
            x=Date,
            color=Province_State))+ 
  geom_line()+
  transition_reveal(Date)
```



