
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---
-------

### I. Questions on Your Selected Data

Use the data of your own.  Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis. 

### Loading the data

My data is a student performance data set

```{r}
library(tidyverse)
df <- read_delim('C:/Users/student/Documents/R/Math421/student-mat.csv', delim =';')
```




-------

1. Make a plot using `face_wrap` by one categorical variable (`face_wrap(~variable1)`)

```{r}
head(df)
```

```{r}
df  %>% 
  ggplot(mapping=aes(x=age, y=failures))+ 
  geom_col()+
  geom_smooth()+
  facet_wrap(~sex)
```


2. Make a plot using `face_wrap` by two categorical variables (`face_wrap(variable1~variable2)`)

```{r}
df  %>% 
  ggplot(mapping=aes(x=age, y=failures))+ 
  geom_col()+
  geom_smooth()+
  facet_wrap(~sex~activities)
```


3. Make a plot using `position ='jitter'`. 

```{r}
df %>% ggplot()+ 
  geom_point(mapping=aes(x=freetime, y=absences, color=sex), 
             position='jitter')
```


4. Make a plot using `position ='dodge'`.

```{r}
df %>% ggplot()+ 
  geom_point(mapping=aes(x=freetime, y=absences, color=sex), 
             position='dodge')
```


5. Make a plot using `position ='fill'`. 

```{r}
df %>% ggplot()+ 
  geom_point(mapping=aes(x=freetime, y=absences, color=sex), 
             position='fill')
```


6. Make a plot using `geom_col`.

```{r}
df %>% ggplot()+ 
  geom_col(mapping=aes(x=age, y=absences, fill=sex), 
             )
```


7. Change the theme of one of your plots. 

```{r}
df %>% ggplot()+ 
  geom_col(mapping=aes(x=age, y=absences, fill=sex)) + theme_dark()
```


8. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md

```{r, eval=FALSE}
gg <- df  %>% 
  ggplot(mapping=aes(x=age, y=failures))+ 
  geom_col()+
  geom_smooth()+
  facet_wrap(~sex)
ggsave(filename = 'abc.png', plot = gg)


```


### II. Questions on Covid Vaccination Data

In this section of questions, we will use  the covid vaccination data for the US. The data and data dictionary can be found at the below link:

- [Data](https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv)

- [Data Dictionary](https://github.com/govex/COVID-19/blob/master/data_tables/vaccine_data/us_data/data_dictionary.csv)


```{r}
library(tidyverse)
df <- read_csv('https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv')
```

1. Put titles, captions, appropriate labels on x and y-axis for the last two questions in Assignments 6.
```{r}
library(lubridate)
df$Month <-  factor(month(df$Date, label = TRUE))

d2 <- df%>% filter(Vaccine_Type!=('All'), Province_State == c("Rhode Island", "Maine", "New Hampshire", "Massachusetts", "Connecticut", "Vermont")) %>% group_by(Vaccine_Type, Month) %>% summarise(doses = mean(Doses_admin))

# Plot from the newly create data
d2 %>% ggplot()+geom_col(mapping=aes(x=Month, y=doses, fill=Vaccine_Type))+scale_y_log10() + labs(x='Month', 
       y = 'Doses Administered', 
       title = 'Popularity of Vaccines in NE', 
       caption = 'Pfizer appears to be the constant most popular vaccine type over the course of the year.')
```


```{r}
# Create a dataset recording these two vaccine administered by state in ne
d2 <- df %>% filter(Vaccine_Type!=('All'), Province_State == c("Rhode Island", "Maine", "New Hampshire", "Massachusetts", "Connecticut", "Vermont"))%>% group_by(Date, Province_State) %>% summarise(vac_admin=mean(Doses_admin, na.rm=TRUE))

# Plot from the newly create data
d2 %>% ggplot()+geom_line(mapping=aes(x=Date, y=vac_admin, color=Province_State)) + labs(x='Month', 
       y = 'Vaccines Administered', 
       title = 'Vaccines Administered by Date in NE', 
       caption = 'Massachusetts is the front runner in vaccine administrations.') 
```


2. Since the data seems lack of categorical variables, we will create a few categorical variables for easier visualization. From the `Date` variable create three categorical variables to record weekdays, months and quarters. You could also create a categorical variable to record the state regions (South, North East, Midwest, West) or other new categorical variables.
```{r}
library(lubridate)
df$Date <- ymd(df$Date)

df$month = month(df$Date)

df$weekday = wday(df$Date)

df$quarter = quarters(df$Date)

```


3. With the updated data after question 2.  Create at least 7 new meaningful graphs.  Your graphs should have titles, captions, appropriate labels on x and y-axis. You should also make use of the follows. 

 - geom_point
 
```{r}
df2 <- df %>% filter( Vaccine_Type=='All') %>% group_by(quarter) %>% summarise(Doses_admin = mean(Doses_admin, na.rm = TRUE))


df2 %>% ggplot()+
  geom_point(mapping = aes(y= Doses_admin, x=quarter)) + labs(title = "Numbers of Doses Administered by Quarter", caption = "Quarter 3 appears to have the highest frequency of doses administered", y= "Doses Administered")

```
 
 - geom_line
```{r}
df %>% ggplot()+
  geom_line(mapping = aes(x= Doses_shipped, y=Doses_admin)) + labs(title="Doses Shipped vs Doses Administered", x = " Doses Shipped", y= "Doses Administered", caption = "The two have a clear positive linear relationship")

```
 
 - geom_smooth
```{r}
df %>% ggplot()+
  geom_smooth(mapping = aes(x= Doses_shipped, y=Doses_admin)) + labs(title="Doses Shipped vs Doses Administered", x = " Doses Shipped", y= "Doses Administered", caption = "The two have a clear positive linear relationship")
```
 
 _ geom_bar
```{r}
df %>% ggplot()+ 
  geom_bar(mapping=aes(x=quarter)) + labs (title = "Number of Records per Quarter", caption= "We only have complete data for quarters 2 and 3.")
```
 
 
 - geom_col
 
```{r}

df2 <- df  %>% group_by(quarter, Vaccine_Type) %>% summarise(Doses_admin = mean(Doses_admin, na.rm = TRUE))


df2 %>% ggplot()+
  geom_col(mapping = aes(y= Doses_admin, x=quarter, fill=Vaccine_Type)) + labs(title = "Numbers of Doses Administered by Quarter", caption = "Quarter 3 appears to have the highest frequency of doses administered", y= "Doses Administered")
```
 
 - face_wrap
```{r}
head(df)
df %>% filter(Province_State == c("Rhode Island", "Maine", "New Hampshire", "Massachusetts", "Connecticut", "Vermont")) %>%
  ggplot()+ 
  geom_bar(mapping=aes(x=quarter)) +
  facet_wrap(~Province_State)
```
 
 - combination of geom_point and geom_smooth 
```{r}
df %>% 
  ggplot(mapping = aes(x= Doses_shipped, y=Doses_admin)) + geom_point() + geom_smooth() + labs(title="Doses Shipped vs Doses Administered", x = " Doses Shipped", y= "Doses Administered", caption = "The two have a clear positive linear relationship")
```
 
